### 2017-03-12 conclusion.tex
Got the first bit of the conclusion re-write done

In this thesis we have explored the effects of SN feedback in the formation of 
galaxies like our own.  We introduced a novel model for SN feedback that
takes into account the important effects of previously ignored physics: the
evaporation of cold gas driven by thermal conduction.  This model allowed us to
see when SN can (and cannot!) regulate the flow of gas into and out of galaxies,
where it ultimately forms stars.  We have also shown that the current $\Lambda
CDM$ cosmological model is consistent with recent observations of galaxy
kinematics.

In Chapter 2, we presented a detailed description of the new superbubble model,
and implemented it in the SPH code {\sc Gasoline2}.  We rely on the strongly
self-limiting process of thermal evaporation \citep{Cowie1977}, where cold mass
is evaporated into a hot bubble at a rate strongly dependent on the temperature
of the hot bubble. This allows us to develop a new model for SN feedback, that gives
realistic estimates for cooling in unresolved hot bubbles, and accurately
calculates the mass loading of SN energy.  We demonstrated that this model is
insensitive to resolution, unresolved ISM structure, and uncertain (turbulent)
magnetic fields.  Finally, after investigating the behaviour of individual
bubbles, we showed that superbubble feedback was more effective at both
regulating star formation and at driving galactic winds.

Isolated disc simulations, like that shown in chapter 2, lack a full
cosmological history.  To really see how SN feedback can impact the overall
growth and history of a galaxy like the Milky Way, we needed to simulate the
galaxy from high redshift to the present, using a zoom-in technique like that
first introduced in \citet{Navarro1993}.  In chapter 3, we compared a Milky
Way-like galaxy, simulated four times with different feedback models (no
feedback, the older \citet{Stinson2006} blastwave model, and superbubble
feedback with $10^{51}\;\rm{erg}/SN$ and $2\times10^{51}\;\rm{erg}/SN$).  The
results of this comparison found that even though the galaxy massively
overproduced stars when simulated without feedback, or with blastwave feedback
(a result previously seen in \citealt{Stinson2010}) , the same SN energy, when
simulated using our new superbubble model, was able to produce a realistic
stellar mass fraction for the galaxy's entire history.  Not only did the galaxy
simulated with superbubble feedback have the correct stellar mass, we showed
that it also was effectively bulgeless, with a completely flat rotation curve.
These two results were ultimately caused by the same process.  At high redshift,
superbubble feedback efficiently drives highly mass loaded winds, expelling gas
from the ISM of the galaxy.  As the gas that forms a stellar bulge was primarily
accreted at high redshift, this meant that these winds preferentially removed
low angular momentum material, while preserving the gas with high angular
momentum.  Thus, superbubble feedback was able to naturally prevent both runaway
star formation and the formation of a bulge through these winds.

While a single galaxy can be a useful case study, multiple objects must be
studied in order to look at population-scale effects.  Chapter 4 extends the
results of chapter 3 by simulating an additional 17 objects, and uses these
simulations to examine if SN regulation can operate effectively in galaxies both
heavier and lighter than the Milky Way.  By creating a new sample of 18
simulated galaxies (the McMaster Unbiased Galaxy Simulations 2), we were able to
demonstrate a critical mass at which SN feedback breaks down as a regulator of
gas accretion and star formation.  Galaxies that exceed this mass, $(\sim
10^{12}\Msun)$, will produce more stars than real galaxies, and produce much
of these stars in a dense stellar bulge.  All of this arises due to a
fundamental relation between the mass loading of superbubble driven winds and
the mass of the galaxy (we found a relation between both disc and halo mass and
$\eta$).  When the escape velocity of the disc exceeds the sound speed of
superbubble-heated gas (which has a typical mass loading of $\eta=10$), only
outflows which have entrained less material are able to escape the galaxy,
leading to decreasing efficiency in ejecting material, and a shutdown of 
regulation.  The fact that this shutdown occurs exactly as powerful AGN are
observed, and that it results in a vigorous transport of gas to the nucleus of
the galaxy make this result strong evidence that this shutdown acts as a 
``hand-off'' between SN and AGN feedback.

The MUGS2 simulations produced in chapter 4 contains a wealth of data that is
useful for future studies. Chapter 5 applied the MUGS2 sample of galaxies we
produced in \citet{Keller2016a} and used them to examine the radial acceleration
relation (RAR) that was derived by \citet{McGaugh2016} from observations of the
SPARC \citep{Lelli2016b} catalog.  The tight relation seen in the SPARC data
does not require new fundamental physics (such as self-interacting dark matter,
modified gravity, or MOND).  Instead, the simple combination of dissipational
collapse, together with angular momentum conservation produces the RAR. This
means that even galaxies where SN fails to regulate their star formation (or
even where SN are omitted altogether) fall on the observed relation.  This was
the first published demonstration of this in simulations, using untuned
simulations made prior to the publication of \citet{McGaugh2016}.

This thesis has shown that, with correct modelling, SN feedback can regulate the
growth of galaxies up to the mass of the Milky Way, but no further.  In galaxies
up to this mass, SN efficiently drive galactic winds, primarily at
high redshift, that act to limit the availability of low angular momentum gas,
slowing the formation of stars and the stellar bulge. Without the
feedback from SMBHs, galaxies more massive than ours form far too many stars,
and primarily form those stars in a concentrated central bulge.  This transition
from SN to AGN feedback occurs due to a rapid drop in the effectiveness of
SN-driven outflows.  Finally, we showed that independent of the detailed
internal processes of galaxy evolution, the acceleration relation observed by
\citet{McGaugh2016} is simply a natural consequence of galaxy formation.

>>>>

In this thesis we have explored the effects of SN feedback in the formation of 
galaxies like our own.  We introduced a novel model for SN feedback that
takes into account the important effects of previously ignored physics: the
evaporation of cold gas driven by thermal conduction.  This model allowed us to
see when SN can (and cannot!) regulate the flow of gas into and out of galaxies,
where it may forms stars.  We have also shown that the current $\Lambda
CDM$ cosmological model is consistent with recent observations of galaxy
kinematics.

In Chapter 2, we presented a detailed description of the new superbubble model,
implemented in the SPH code {\sc Gasoline2}.  We rely on the strongly
self-limiting process of thermal evaporation \citep{Cowie1977}, where cold mass
is evaporated into a hot bubble at a rate strongly dependent on the temperature
of the hot bubble. This drives the interior of the bubble to a temperature of a
few $10^6$ K, evaporating material more or less rapidly as the temperature dips
above or below this value.  This is the characteristic temperature for SN-heated
gas.  We use this physics to develop a new model for SN feedback, that gives
realistic estimates for cooling in unresolved hot bubbles, and accurately
calculates the mass loading of SN energy.  We demonstrated that this model is
insensitive to resolution, unresolved ISM structure, and uncertain (turbulent)
magnetic fields.  The strong temperature dependence of thermal evaporation means
that significant changes to the conduction rate (such as the supression by
magnetic fields) result in only slight changes to the temperature of
feedback-heated gas.  Finally, after investigating the behaviour of individual
bubbles, we showed that superbubble feedback is more effective at both
regulating star formation and at driving galactic winds.

Isolated disc simulations, like that shown in chapter 2, lack a full
cosmological history.  To see how SN feedback can impact the overall growth and
history of a galaxy like the Milky Way, we needed to simulate the galaxy from
high redshift to the present.  In chapter 3, we use zoom-in cosmological
simulations \citet{Navarro1993} of a Milky Way-like galaxy to compare the
effects of different feedback models.  The galaxy, when simulated using our new
superbubble model, was able to produce a realistic stellar mass fraction for the
galaxy's entire history.  Not only did the galaxy simulated with superbubble
feedback have the correct stellar mass, we showed that it also was effectively
bulgeless, with a completely flat rotation curve.  These two properties arose
via a single process.  At high redshift, superbubble feedback efficiently drives
heavily mass loaded winds, expelling gas from the ISM of the galaxy.  The gas
that forms a stellar bulge is accreted at high redshift, meaning that these
winds preferentially remove low angular momentum material, while preserving the
gas with high angular momentum.  Thus, superbubble feedback is able to naturally
prevent both runaway star formation and the formation of a bulge through these
winds.

While a single galaxy can be a useful case study, multiple objects must be
studied in order to look at population-scale effects.  Chapter 4 extends the
results of chapter 3 by simulating an additional 17 objects, and uses these
simulations to examine if SN regulation can operate effectively in galaxies both
heavier and lighter than the Milky Way.  With this new sample (the McMaster
Unbiased Galaxy Simulations 2), we were able to demonstrate a critical mass at
which SN regulation of gas accretion and star formation breaks down.  Simulated
Galaxies that exceed this mass, $(\sim 10^{12}\Msun)$, overproduce stars,  most
of which form in a dense stellar bulge.  All of this arises due to a fundamental
relation between the mass loading of superbubble driven winds and the mass of
the galaxy.  When the escape velocity of the disc exceeds the sound speed of
superbubble-heated gas (which has a characteristic temperature of
$\sim3\times10^6$ K), only outflows which have entrained less material are able
to escape the galaxy. This leads to less gas ejection, and a shutdown of
regulation.  The fact that this shutdown occurs exactly at the galaxy mass where
powerful AGN are observed, and that it results in a vigorous transport of gas to
the nucleus of the galaxy make this result strong evidence that this shutdown
is a key component in the ``hand-off'' between SN and AGN feedback.

The MUGS2 simulations produced in chapter 4 contains a wealth of data useful for
future studies. Chapter 5 applied the MUGS2 galaxies produced in
\citet{Keller2016a} to examine the radial acceleration relation (RAR) derived by
\citet{McGaugh2016} from observations in the SPARC \citep{Lelli2016b} catalog.
We found that the tight relation seen in the SPARC data does not require new
fundamental physics (such as self-interacting dark matter, modified gravity, or
MOND).  Instead, the simple combination of dissipational collapse, together with
angular momentum conservation produces the RAR. This means that even galaxies
where SN fails to regulate their star formation (or even where SN are omitted
altogether) fall on the same observed relation.  This was the first published
demonstration of this in simulations, using untuned simulations made prior to
the publication of \citet{McGaugh2016}.

This thesis has shown that, with correct modelling, SN feedback can regulate the
growth of galaxies up to the mass of the Milky Way, but no further.  In galaxies
below this mass, SN efficiently drive galactic winds, primarily at
high redshift, that act to limit the availability of low angular momentum gas,
slowing the formation of stars and the stellar bulge. Without the
feedback from SMBHs, galaxies more massive than ours form far too many stars,
and primarily form those stars in a concentrated central bulge.  This transition
from SN to AGN feedback occurs due to a rapid drop in the effectiveness of
SN-driven outflows.  Finally, we showed that independent of the detailed
internal processes of galaxy evolution, the acceleration relation observed by
\citet{McGaugh2016} is simply a natural consequence of galaxy formation.
